Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}

### 2020-07-02 large_experiment_processing.Rmd
Update large_experiment_processing.Rmd
Co-authored-by: Sebastian Gibb <mail@sebastiangibb.de>

The `fromFile` function can be used to determine the source file (sample)
of a specific spectrum in the `MSnExp` object. This function returns an `integer`
vector, of the same length as spectra in the experiment, with the file index. The
file names can be accessed with the `fileNames` method. A `MSnExp` object can be
subsetted with `[` and e.g. the index of the spectra that should be retained. In
the code block below we subset our `ms_dsk` object to contain only spectra from
the 3rd file.

@@

Note however that there are also dedicated *filter* functions to subset an
`MSnExp` object such as `filterFile`, `filterMsLevel`, `filterRt`, `filterMz`,
`filterPrecursorMz` or `filterIsolationWindow`. In the example below we use the
`filterRt` function to further subset our data to contain only spectra acquired
within a certain time range.

>>>>

The `fromFile` function can be used to determine the source file (sample)
of a specific spectrum in the `MSnExp` object. This function returns an `integer`
vector, of the same length as spectra in the experiment, with the file index. The
file names can be accessed with the `fileNames` method. An `MSnExp` object can be
subsetted with `[` and e.g. the index of the spectra that should be retained. In
the code block below we subset our `ms_dsk` object to keep only spectra from
the 3rd file.

@@

Note that there are also dedicated *filter* functions to subset an
`MSnExp` object such as `filterFile`, `filterMsLevel`, `filterRt`, `filterMz`,
`filterPrecursorMz` or `filterIsolationWindow`. In the example below we use the
`filterRt` function to further subset our data to contain only spectra acquired
within a certain time range.
